---
title: "Assignment_3_LIURUOBING"
author: "LIURUOBING"
date: "2022-11-03"
output: word_document
---

## install.packages("tidyr")

```{r}
library(tidyr)
```

## Download the file price_index_Feb20201 and name it "price"

```{r}
price <- read.csv("C:/Users/13711/Desktop/price_index_Feb20201.csv")
```

##View the data

```{r}
price
```

##View the first five rows of data

```{r}
head(price,n=5)
```

##View the last four rows of data

```{r}
tail(price,n=4)
```

##Display the number and name of the data set variables

```{r}
names(price)
```

##View "price" data summary #We can see the name of each column of this data set, as well as the length of each column, the data classification type, and the data pattern type #From the summary of this data set, there are 10 columns, all 1203 in length, where the columns named TIME_REF and DATA_VAL are of numeric type, all of which have maximum value, minimum value, average and quartiles.

```{r}
summary(price)
```

##Show the complete structure of the data

```{r}
str(price)
```

##Quantifying the sample quantile of a variable for a given sample #According to the result, you can see how much data is in each quantile of the variable "DATA_VAL" of this sample

```{r}
quantile(price$DATA_VAL,na.rm=T)
```

##Used to detect the presence of missing values in the observation column

```{r}
sum(is.na(price$DATA_VAL))
```

##Used to monitor this dataset for missing values

```{r}
colSums((is.na(price)))
all(colSums(is.na(price))==0)
```

##Used to find the value of specific characters #According to the setting, I can learn that the number of variables that are 1000 or 1133 in the variable DATA_VAL is 12, and the number of variables that are not is 1191

```{r}
table(price$DATA_VAL %in% c("1000","1133"))
```

##Find the location of a particular observation and export it as a new data set

```{r}
Specdata <- price[price$DATA_VAL %in% c("1000","1133"),]
Specdata
```

##If the test value is valid, output good, otherwise output bad

```{r}
newprice <- ifelse(
    price$DATA_VAL>1100,"good",
    ifelse(
        price$DATA_VAL<1000,"bad",
        "not"
    )
)
newprice
```

##install.packages("Hmisc")

```{r}
library(Hmisc)
```

## Use the cut2() function to segment the data,g is the required number of segments

```{r}
price$DATA_VAL <- cut2(price$TIME_REF,g=4)
table(price$TIME_REF)
```

####################################### 

##install.packages("plyr")

```{r}
library(Hmisc)
library(plyr)
price$Series_title_1 <- factor(price$Series_title_1)
price$Series_title_1
```

##Sort DATA_VAL by Series_title_1 and name the generated list as x

```{r}
x <- split(price$DATA_VAL,price$Series_title_1)
```

##Use the sapply function to average the list of x

```{r}
sapply(x, mean)